Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
describing reusable spec.

>>>>

\begin{itemize}
\item Some type classes have their laws.
\item We can use Hspec to enforce such properties.
\item If such properties are reusable among instances,
we can avoid boilerplates.
\item reusable spec can do this.
\end{itemize}

\begin{quote}
\small
\begin{verbatim}
shouldSatisfyMonoidLaws ::
  (Eq a, Show a, Monoid a, Arbitrary a) => a -> Specs
shouldSatisfyMonoidLaws t = do
  describe "mempty" $ do
    it "is a left identity" $ property $ \x ->
      mempty <> x == x `asTypeOf` t

    it "is a right identity" $ property $ \x ->
      x <> mempty == x `asTypeOf` t

  describe "<>" $ do
    it "is associative" $ property $ \x y z ->
      (x <> y) <> z == x <> (y <> z) `asTypeOf` t
\end{verbatim}
\end{quote}

\noindent The following is an example to apply this laws
to lists.

\begin{quote}
\small
\begin{verbatim}
describe "List as a Monoid" $
  shouldSatisfyMonoidLaws (undefined :: [Int])
\end{verbatim}
\end{quote}

\begin{itemize}
\item we should prepare this kind of laws.
\end{itemize}
